\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format

\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{pgfgantt}
\usepackage{float}
\usepackage{natbib}
%SetFonts

%SetFonts

\title{Placing UK Research within the International STEM Funding Landscape}

\begin{document}


\begin{titlepage}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\center
\textsc{\LARGE MSc Project Proposal}\\[1.5cm] % Name of your university/college
\textsc{\Large Imperial College London}\\[0.5cm] % Major heading such as course name
\textsc{\large Computational Methods in Ecology and Evolution}\\[0.5cm] % Minor heading such as course title
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------
\makeatletter
\HRule \\[0.4cm]
{ \huge \bfseries \@title}\\[0.4cm] % Title of your document
\HRule \\[1.5cm]
 
%----------------------------------------------------------------------------------------
%	AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{0.4\textwidth}
\begin{flushleft} \large
\emph{Author:}\\
Xuan Wang % Your name
\end{flushleft}
\end{minipage}
~
\begin{minipage}{0.4\textwidth}
\begin{flushright} \large
\emph{Leading Supervisor:} \\
Dr. Samraat S. Pawar \\[1.2em] % Supervisor's Name
\emph{Other Supervisor:} \\
W. D. Pearse
\end{flushright}
\end{minipage}\\[2cm]
\makeatother

{\large \today}\\[2cm] % Date, change the \today to a set date if you want to be precise

\vfill % Fill the rest of the page with whitespace

\end{titlepage}
					% Activate to display a given date or no date

\maketitle

\section{Introduction and Proposed Questions}

The funding strategy for STEM discipline differs among countries, leading to differences in their development and contribution to the world. Nevertheless, it is not uncommon that bias sometimes affects the distribution of research funding [\cite{crudden2022gender}]. Therefore, studying the base of bias in research funding could be beneficial to understand the current research funding distribution and gaining a more objective result.

\bigbreak
\noindent In my project, we aim to find the answer to the question: Is there any bias within the international STEM funding landscape? In particular, this question will be answered from the following aspects: [\cite{wojick2015government}]

\begin{itemize}
\item Gender bias - What is the proportion of each gender being funded in each field?
\\As one of the most prevalent topics in the academic thing, gender disparities have drawn a lot of attention. A research of Romy Lee and Naomi Ellemiers [\cite{van2015gender}] has revealed the existence of a research funding gap between different genders, which leads to an underrepresentation of females in academia. Therefore, gender bias would be an essential scale to measure in our report.
\item Avoiding risky projects - 1. What is defined as ``risky"? 2. Regarding the risky projects, how many of them are funded?
\\Due to financial constraints, the "risk" of a proposal is usually a critical point in whether the project will be funded. The proposal reviewers are generally less likely to fund a project with some errors or an idea that seems too outlandish, while sometimes these projects can be a revolutionary piece of work [\cite{franzoni2022funding}]. This raises the concern about the decreasing number of innovative and risky grant proposals [\cite{severin2021research}], and therefore will also be included in our study.
\item Racial bias - What is the ratio of applicants with different races being funded in the fields?
\\Disparities among funding for different races and ethnicities have been a more "invisible" bias compared to the others. According to the data reported in 2013, around 23.3\% of white applicants received funding from the National Institutes of Health (NIH), while the percentage for nonwhite applicants is 19.3\% [\cite{konkel2015racial}]. A significant difference has persisted for the past few decades, reducing the diversity in science. This bias should be taken into consideration as well.
\end{itemize}


\section{Methodology}
Fine-scale data will be used for our project. Mallet will be applied for the Machine Learning procedure. As the countries with the highest GDP worldwide, we will use the data from Australia, Canada, European Union, India, New Zealand, the United Kingdom, and the United States of America. In addition to the existing data we have, the data from China needs to be collected, which can be retrieved from public resources of China such as the website of National Data: https://data.stats.gov.cn/index.htm. 
We will apply pre-processing to the raw data, and the clean fine-scale data will be used for the analysis. HPC could be employed if the data is too big; the results from different countries will be compared for the final analysis.

\section{Anticipated outputs and outcomes}

\begin{itemize}
\item The bias in research funding in a set of countries will be displayed concerning countries respectively;
\item For each type of bias, the result for different countries will be taken into comparison;
\item Analysis will be conducted regarding the potential reason and consequence of the biases.

\end{itemize}

\section{Project Feasibility}

The timeline for this project is displayed as follows:

\begin{figure}[htbp]

\begin{center}

\begin{ganttchart}[y unit title=0.4cm,
y unit chart=0.5cm,
vgrid,hgrid, 
title label anchor/.style={below=-1.6ex},
title left shift=.05,
title right shift=-.05,
title height=1,
progress label text={},
bar height=0.7,
group right shift=0,
group top shift=.6,
group height=.3]{1}{20}
%labels
\gantttitle{Month}{20} \\
\gantttitle{April}{4} 
\gantttitle{May}{4} 
\gantttitle{June}{4} 
\gantttitle{July}{4} 
\gantttitle{August}{4} \\
%tasks
\ganttbar{Review literature} {1}{4}\\
\ganttbar{Find data}{3}{5} \\
\ganttbar{Data pre-processing}{5}{8} \\
\ganttbar{Applying machine learning approaches}{9}{16} \\
\ganttbar{Write up}{5}{20} \\



\end{ganttchart}
\end{center}
\caption{Gantt Chart}
\end{figure}

\noindent The writing will be covered throughout most of the time. The aim is to complete the first write-up by early August, and then modify it for the rest of the weeks. 

\pagebreak

\bibliographystyle{agsm}
\bibliography{Proposal}

\end{document}  